Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Several efforts made to correct bad spacing. Eventually, this seems to have been caused by the stfloats package.
Also now using subcaption package.
Also removed some redundant preamble content.

% *** MISC UTILITY PACKAGES ***
%
\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
   % pdf code
 %\else
   % dvi code
% \fi

% *** CITATION PACKAGES ***
%
\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}

\usepackage{stfloats}

@@

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}

@@

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

\usepackage{todo}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=3in]{overview.png}
	\caption{Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)}
	\label{fig:ANITAoverview}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at the SUP.
        Concentric white circles indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
    \caption{
        Neutron profile at the SUP, normalised to fluence rate on axis.
        Vertical lines indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPProfile}
\end{figure}

Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
The results show\ldots\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}

\begin{figure}[t]
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}}\\
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
The results show\ldots\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

Fig.~\ref{fig:CUPSpectraCOmparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
The results show\ldots\todo{Explain what the results show: CUP measurement comparison.}
Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
The results show\ldots\todo{Explain what the results show (comparison between independent MC calculations).}

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \todo{Show Comparison between Geant4 and MCNPX calculations}
    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}}
    \label{fig:MCComparison}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
    \caption{Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}}
    \label{fig:DifferentialSpectra}
\end{figure}

\subsection{Neutron time of flight}

Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
Our Geant4 model permits these measurements to be simulated.
Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
Results are for SUP and CUP-TOF positions and compared with measurements~\cite{Prokofiev2009,Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
The results show\ldots\todo{Explain what the results show.}

\begin{figure}[!t]
	\centering
	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
	\label{fig:TOFFrameOverlapspectrum}}\\
	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
	\label{fig:SUP10FrameOverlapspectrum}}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=3in]{TOF3Componentslinear.eps}
	\caption{
    Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position.
    The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.}
	\label{fig:TOF3Componentslinear}
\end{figure}

\subsection{Gamma fluence rate, spatial distribution and dose rate}

Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
The results show\ldots\todo{Describe the gamma results}

\begin{figure}[t]
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	SUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
%    CUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

\usepackage{ifpdf}
\usepackage{cite}

\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi

\usepackage[cmex10]{amsmath}

\usepackage{array}
\usepackage{fixltx2e}

@@

\usepackage{url}

@@

\usepackage{booktabs}

\usepackage{graphicx}
\usepackage{epstopdf}

\usepackage{caption}
\usepackage{subcaption}
\captionsetup{margin={0pt,20pt}}
\captionsetup[sub]{margin={0pt,20pt}}

\usepackage{todo}
%\renewcommand\todo[1]{\relax}
%\renewcommand\todos{\relax}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{overview.png}
	\caption{
        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)
    }
	\label{fig:ANITAoverview}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=2.5in]{SUP10ColSpatialDistribution10MeVRADECS.png}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at the SUP.
        Concentric white circles indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=2.5in]{SUP10beamproFoldingRADECS.png}
    \caption{
        Neutron profile at the SUP, normalised to fluence rate on axis.
        Vertical lines indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPProfile}
\end{figure}

Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
The results show\ldots
\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=2.5in]{ANITAIntYieldRADECS.eps}
        \subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=2.5in]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
    }
	\label{fig:SUPSpectraComparison}
\end{figure}

Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=2.5in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the CUP}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=2.5in]{CUPTOF10beamproRADECS.png}
    % \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the CUP}
    \label{fig:CUPProfile}
\end{figure}

Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
The results show\ldots
\todo{Explain what the results show: CUP measurement comparison.}
Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
The results show\ldots
\todo{Explain what the results show (comparison between independent MC calculations).}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \todo{Integral spectra on log-log axes: CUP}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
    	\subcaption{Integral fluence rate}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
        \todo{Normalised spectra on lethargy axes: CUP}
    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
    \end{minipage}
	\caption{
        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
    }
	\label{fig:CUPSpectraComparison}
\end{figure}

\begin{figure}[t]
    \todo{Show Comparison between Geant4 and MCNPX calculations}
    %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
    \caption{
        Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}
    }
    \label{fig:MCComparison}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=2.5in]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

\subsection{Neutron time of flight}
Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
Our Geant4 model permits these measurements to be simulated.
Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
Results are for SUP and CUP-TOF positions and compared with measurements~\cite{Prokofiev2009,Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
The results show\ldots\todo{Explain what the results show.}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \todo{Add experimental data to TOF figure (CUP)}
        \includegraphics[width=2.5in]{TOF3frameoverlap.eps}
        \subcaption{At the CUP-TOF position, with \SI{3}{\cm} collimator}
    	\label{fig:TOFFrameOverlapspectrum}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \todo{Add experimental data to TOF figure (SUP)}
        \includegraphics[width=2.5in]{SUP10frameoverlap.eps}
        \subcaption{At the SUP, with \SI{10.2}{\cm} collimator}
        \label{fig:SUP10FrameOverlapspectrum}
    \end{minipage}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{TOF3Componentslinear.eps}
	\caption{
        Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position.
        The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.
    }
	\label{fig:TOF3Componentslinear}
\end{figure}

\subsection{Gamma fluence rate, spatial distribution and dose rate}
Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
The results show\ldots\todo{Describe the gamma results}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
        \subcaption{SUP}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
        \subcaption{CUP}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=2.5in]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
        \subcaption{SUP}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
        \subcaption{CUP}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}
